Flexibility of interactions depends on habitat suitability

### 2019-09-01 paper/manuscript.Rmd
"Finish off" intro P4

After community composition has been determined, one way the environment can influence wether two species interact or not is by affecting their Eltonian-niche [@tylianakis_ecological_2017]. 
This effect can happen through what we call stress/suitability-induced hypotheses of interaction turnover. 
The first hypothesis is that when species are under environmental stress, they might be "pressured" to focus on the partners with which they are best adapted to interact. 
For instance @peralta_phylogenetic_2015 found that parasitoids in plantation forest, where enviornmental stress were higher than in native forests, were constrained to attack only hosts they were best adapted to. 
Similarly, @lavandero_genotype_2013 found that environmental stress due to higer temperature reduced the breadth of the Eltonian niche of parasitoids. 
The alternative hypotheis is that when species are under environmental stress they are forced

>>>>

After community composition has been established, one way the environment can influence whether two species interact or not is by affecting their Eltonian-niche [@tylianakis_ecological_2017]. 
This effect can happen through what we call stress/suitability-induced hypotheses of interaction turnover. 
The first hypothesis is that when species are under environmental stress, they might be "pressured" to focus on the partners with which they are best adapted to interact. 
For instance, @hoiss_altitude_2012 found increased phylogenetic clustering between plants and pollinators at higher altitudes; while @peralta_phylogenetic_2015 found that parasitoids in plantation forest, where environmental stress was higher than in native forests, were constrained to interact with hosts, they were best adapted to attack.
Similarly, @lavandero_genotype_2013 found that environmental stress due to higher temperature reduced the breadth of the Eltonian niche of parasitoids. 
An alternative hypothesis is that when species are under environmental stress, they are forced to be more flexible in their interactions as higher environmental stress is likely to be reflected in greater energetic or reproductive costs and therefore they might not be able to sustain encounter rates with their preferred partners at sufficient levels. 
For instance, @hoiss_interactive_2015 found that the specialization of plant-pollinator networks decreased both with elevation and after extreme drought events.
Likewise, @pellissier_spatial_2010 found a positive relationship between niche breadth and environmental stress: disk- or bowl-shaped blossoms (which allow a large number of potential pollinator species to access pollen and nectar rewards) dominated at high altitude flower communities.

Here, we expli
Benadi found that

Generalists vs specialists might show contrasting patterns.

Here we

Specialist species (that lack flexibility in their choice of interaction partner) should theoretically be most vulnerable to phenological decoupling. However, one study of pollinator communities along an elevational gradient found that apparently specialized pollinators were facultatively more generalist than they appeared and could adapt their visitation patterns across sites as much as generalists to avoid phenological asynchrony (Benadi et al. 2014). Similarly, duration of the fruiting season has been shown to predict the degree and strength of seed-dispersal interactions (Gonza ́ lez- Castro et al. 2012), and a long-term study found no difference between specialist and generalist plant species in their interannual fluctuations in phenology and pollinator richness (Petanidou et al. 2014). Although these findings suggest that the facultative generalism of pollination mutualisms may confer robustness to these networks in the face of altered phenology (see also discussion on rewiring above), this robustness may depend on the climate context and the diversity and specialization within the network (Hoiss et al. 2015). Moreover, less-generalized interactions such as those between parasites and hosts may show less flexibility.
